Exploring Factors Influencing Average Playtime of Video Games: A Regression Analysis

### 2024-12-01 paper/paper.Rmd
fix a typo

y_hat <- fitted(model_1)
plot(x = y_hat, y = data$average_playtime, main = "Response vs. Fitted", xlab = "Fitted", ylab = "Average Playtime")
abline(a=0, b=1, lty=2)
```
To check the conditional mean response assumption, we analyze the Response vs. Fitted scatterplot @fig-resp-fit. The data points are tightly clustered in the bottom-left corner, which satisfies this assumption. The fitted line generally follows the line $y=hat{y}$, but there are notable outliers along the Y-axis where the observed `average_playtime` deviates significantly from the predicted values. These extreme outliers suggest that the response variable may be highly skewed or contain problematic data points.

>>>>

y_hat <- fitted(model_1)
plot(x = y_hat, y = data$average_playtime, main = "Response vs. Fitted", xlab = "Fitted", ylab = "Average Playtime")
abline(a=0, b=1, lty=2)
```
To check the conditional mean response assumption, we analyze the Response vs. Fitted scatterplot @fig-resp-fit. The data points are tightly clustered in the bottom-left corner, which satisfies this assumption. The fitted line generally follows the line $y=\hat{y}$, but there are notable outliers along the Y-axis where the observed `average_playtime` deviates significantly from the predicted values. These extreme outliers suggest that the response variable may be highly skewed or contain problematic data points.
